\textit{Urban and building multiscale co-simulation: case study implementations on two university campuses}

### 2016-04-14 latex/UMEM_CoSim.tex
Update paper with latest results graphics
Updated both case studies graphics from the python-notebook folders.
Right now this is manual, but soon the notebooks will dump their
graphics directly into the right folders

\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
\usepackage{subfigure}% Support for small, `sub' figures and tables
\usepackage{lmodern}
\usepackage{color}
\usepackage[utf8]{inputenc}
\usepackage{float}

@@

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.7]{figures/UMEM_Workflow}
\caption{Overview diagram of the coupling process including tools and outputs}
\label{fig:OverallWorkflowProcess}
\end{figure}

@@

\subsection{Model development}
In order to perform a co-simulation of the targeted buildings, initially a CitySim model of the campus is developed as seen in Figure \ref{fig:campuscitysim}. 
% An existing EnergyPlus model is used for the HPZ building and simplified single-zone EnergyPlus models are extracted from the CitySim geometry for the other three targeted buildings.

@@

\subsection{Measured data collection and processing}
% Energy data from each of the targeted buildings is collected and analyzed in the context of the simplified calibration procedures. The measured datasets are screened and aggregated into typical usage profiles to be used for the lighting, plug-loads, and HVAC equipment availability schedules and power densities. Figures \ref{fig:hpz_profiles}-\ref{fig:hit_profiles} illustrate the aggregation examples of the heating energy from the HPZ building and the electrical energy from HPK, HPI, and HIT. These profiles were created through a filtering and clustering process known as \emph{DayFilter} \cite{Miller:2015kr}. These profiles are used to set the availability schedules as inputs into the EnergyPlus simulation to emulate the way occupants inhabit the building and how the building management system (BMS) controls the lighting and HVAC systems. This approach is compared to the practice of interviews and site visits to determine such input parameters.

@@

% \begin{figure}
% \centering
% \includegraphics[scale=0.45]{figures/HPI_combinedclusterandcal_4}
% \caption{HPI Electrical Energy Typical Profiles}
% \label{fig:hpi_profiles}
% \end{figure}

@@

\section{Results}

>>>>

\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
\usepackage{subfigure}% Support for small, `sub' figures and tables
\usepackage{lmodern}
\usepackage{color}
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{lineno}

@@

\linenumbers

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.7]{figures/UMEM_Workflow}
\caption{Overview diagram of the coupling process including tools and outputs (adapted from \cite{thomas2014multiscale})}
\label{fig:OverallWorkflowProcess}
\end{figure}

@@

\subsection{Model development}
In order to perform a co-simulation of the targeted buildings, initially a CitySim model of the campus is developed. Through the workflow automation process, this geometry was converted into an EnergyPlus input file as seen in Figure \ref{fig:HPIcampus}. 
% An existing EnergyPlus model is used for the HPZ building and simplified single-zone EnergyPlus models are extracted from the CitySim geometry for the other three targeted buildings.

@@

\subsection{Measured data collection and calibration}

Energy data from the HPI building was collected and analyzed in the context of the simplified calibration procedures. The measured datasets are screened and aggregated into typical usage profiles to be used for the lighting, plug-loads, and HVAC equipment availability schedules and power densities. Figure \ref{fig:hpi_elec_profiles} illustrates the aggregation examples of electrical energy for the HPI building. This profile was created through a filtering and clustering process known as \emph{DayFilter} \cite{Miller:2015kr}. This profile is used to set the availability schedules as inputs into the EnergyPlus simulation to emulate the way occupants inhabit the building and how the building management system (BMS) controls the lighting and HVAC systems. This approach is compared to the practice of interviews and site visits to determine such input parameters.

\begin{figure}[H]
\centering
\includegraphics[scale=0.6]{figures/HPI_combinedclusterandcal_4}
\caption{HPI Electrical Energy Typical Profiles}
\label{fig:hpi_elec_profiles}
\end{figure}

The measured and simulated data from both the co-simulation and EnergyPlus solo simulations is shown in Figure \ref{fig:hpi_measvssim}.

\begin{figure}[H]
\centering
\includegraphics[scale=0.55]{figures/HPI_MeasvsSim}
\caption{HPI Measured vs. Co-Simulation and EnergyPlus Solo for Heating and Cooling Seasons}
\label{fig:hpi_measvssim}
\end{figure}

\subsection{EnergyPlus co-simulation results}

\begin{figure}[H]
\centering
\includegraphics[scale=0.55]{figures/HPI_EnergyPlus_Heating}
\caption{HPI Co-Simulation vs. EnergyPlus Solo for Heating}
\label{fig:hpi_energyplusheating}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[scale=0.55]{figures/HPI_EnergyPlus_Cooling}
\caption{HPI Co-Simulation vs. EnergyPlus Solo for Cooling}
\label{fig:hpi_energypluscooling}
\end{figure}

% \ref{fig:hpz_profiles}-\ref{fig:hit_profiles}

@@

@@

% \section{Results}
\subsection{Comparison of EnergyPlus and CitySim}

\begin{figure}[H]
\centering
\includegraphics[scale=0.55]{figures/QN_Cooling}
\caption{Quartier Nord CitySim vs. EnergyPlus Solo for Cooling}
\label{fig:qn_eplusvscitysim_cooling}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[scale=0.55]{figures/QN_Heating.pdf}
\caption{Quartier Nord CitySim vs. EnergyPlus Solo for Heating}
\label{fig:qn_eplusvscitysim_heating}
\end{figure}

\subsection{EnergyPlus Co-simulation results}

\begin{figure}[H]
\centering
\includegraphics[scale=0.55]{figures/QN_EnergyPlus_Cooling}
\caption{Quartier Nord EnergyPlus Co-Simulation vs. Solo for Cooling}
\label{fig:qn_eplus_cosimvssolo_cooling}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[scale=0.55]{figures/QN_EnergyPlus_Heating}
\caption{Quartier Nord EnergyPlus Co-Simulation vs. Solo for Heating}
\label{fig:qn_eplus_cosimvssolo_heating}
\end{figure}

\subsection{CitySim Co-simulation results}

\begin{figure}[H]
\centering
\includegraphics[scale=0.55]{figures/QN_CitySim_Cooling}
\caption{Quartier Nord CitySim Co-Simulation vs. Solo for Cooling}
\label{fig:qn_citysim_cosimvssolo_cooling}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[scale=0.55]{figures/QN_CitySim_Heating}
\caption{Quartier Nord CitySim Co-Simulation vs. Solo for Heating}
\label{fig:qn_citysim_cosimvssolo_heating}
\end{figure}
